MachLLensFinder - I: A Machine Learning Strong Lensing Identification Pipeline

### 2016-11-12 ms.tex
Added stubs for noBCG and FalseIDs subsections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:hogvisual}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\hspace{-20pt}
\caption{Visualized HOG feature vectors of the sample lensed HST-like
  image from Figure~\ref{fig:mockimages}.  Left: The corresponding HOG
  visualization with N$_\text{orient}=5$, (32, 32) pixels per cell,
  and (1, 1) cells per block.  Right: The HOG visualization of the
  same mock image with N$_\text{orient}=9$, (16, 16) pixels per cell,
  and (1, 1) cells per block.  The brightest lines align with
  prominent edges.  Note, while fewer pixels per cell will better
  resolve the arc feature, the ``edge'' corresponding to the arc is
  less prominent.  }
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Logistic regression and regularization
As described in Section~\ref{sec:logreg}, logistic regression trains a
model with complexity determined by the regularization parameter.  The
regularization parameter ultimately defines the model performance.
Figure~\ref{fig:regularization} shows the model performance as a function of
regularization parameter.

% Scores vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:regularization}
\begin{center}
\includegraphics[width=\columnwidth]{figures/ROC_multipleHOG.png}
\caption{}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

Previous works to identify strong lensing systems have often removed
the BCG from images to better identify lensed galaxies.  Here, we

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:hogvisual}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}
\caption{Visualized HOG feature vectors of the sample lensed HST-like
  image from Figure~\ref{fig:mockimages}.  Left: The corresponding HOG
  visualization with N$_\text{orient}=5$, (32, 32) pixels per cell,
  and (1, 1) cells per block.  Right: The HOG visualization of the
  same mock image with N$_\text{orient}=9$, (16, 16) pixels per cell,
  and (1, 1) cells per block.  The brightest lines align with
  prominent edges.  Note, while fewer pixels per cell will better
  resolve the arc feature, the ``edge'' corresponding to the arc is
  less prominent.  }
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Logistic regression and regularization
As described in Section~\ref{sec:logreg}, logistic regression trains a
model with complexity determined by the regularization parameter,
$C_\text{LogReg}$.  Increasing model complexity (larger
$C_\text{LogReg}$), will better describe features in the training
set[wc?].  However, an overly complex model will overfit the training
set at the expense of its performance on any independent test set.
The regularization parameter ultimately defines the model performance,
and we must perform a parameter search to identify the optimal value
for $C_\text{LogReg}$.

Figure~\ref{fig:regularization} shows the model performance as a
function of regularization parameter.  The left panel shows the
accuracy, or score, of the model as a function of regularization
parameter.  The right panel shows the AUC of the model as a function
of regularization parameter.  The solid and dotted lines respectively
correspond to the model performance on the test and training set.

For either characterization of the model, the model performance on the
training set increases and asymptotes with $C_\text{LogReg}$.  With
increasing model complexity, the model better fits the data set it has
been trained on.  This is analogous to fitting a seventh order
polynomial to seven data points, where the fitting function will go
through every point.

EDITING HERE

% Scores vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:regularization}
\begin{center}
\includegraphics[width=\columnwidth]{figures/regularized_accuracy.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/regularized_AUC.pdf}
\caption{Left: Accuracy of the model with varying regularization.
  Each color corresponds to a model trained for features extracted
  with a different set of HOG parameters.  The dotted (solid) lines
  show the performance of the model on the training (test) set.
  Right: AUC of the model with varying regularization.  Linestyles and
  colors are similar to those in the left panel.  AUC is a better
  characterization of model performance, since the accuracy is
  determined for fixed classification threshold [wc?], but peak model
  performance can occur at a different classification threshold.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The best ROC curve, HST:N5ppc32cpb4C100, illustrates that we can lower
the classification threshold and improve the true positive rate by
$\sim10\%$ and sacrifice an increase in false positive rate by
$\lsim5\%$.  In this section, we examine the ``borderline'' images,
which transition from negative classification to positive calculation
in the steepest part of the AUC curve.  Borderline images correspond
to candidates for spectroscopic follow-up.  The model is less
confident about this subset of images, and these would therefore be
good candidates for follow-up human classification and/or
spectroscopic follow-up (CITE HERE???).

\todo{Figure ~\ref{fig:falseids} shows a random sample of 10 borderline
images.  Common features...????}

@@

Previous works to identify strong lensing systems have often modeled
out the BCG from images to better identify lensed images (???CITE
HERE???).  Here, we test the effects of the BCG by training and
testing models on mock data where the BCG has not been included.  By
construction, these results show the maximal improvement that can be
obtained from BCG subtraction.

Figure~\ref{fig:ROCnobcg} shows the \todo{ROC curve for models of HOG
  feature vectors of mock data with no BCG.  The feature vectors are
  the same HOG parameters as in Figure~\ref{fig:ROC} }.  \todo{The
  grid search over parameter space was similar to that for data with
  the BCG.}

???????
